Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2021-01-24 SIR_manuscript.tex
a few more notes

Note that the block matrix $G_{12}$ does not influence $\Rnum$ defined as the spectral radius of $G$. All matters here are the eigenvalues of $G_{11}$, which are 0 and $\Rnum$ \eqref{R0}.

% %%%%%%%
\subsection{On Testing Rate and Numerical Singularity}
The testing rate, $\sigma$, should be formulated such that people from the untested compartments will not be tested if they are not there. The numerical singularity issue with the chosen $\sigma$ \eqref{sigma} is that the population in $S$ compartments appeared to blow up when the DFE is achieved. This is once the only untested people are susceptibles, the FOI will become $\Lambda=0$, testing rate $F_s=\rho N_0/S_u$. Thus, eq(1) of the model will be $d S_u/dt = - \rho N_0 + \omega S_n$ which is no longer dependent on $S_u$ and a linear rate of leaving the $S_u$ compartment.

@@

Note that in case of ``perfect isolation``, i.e., when $\eta_w=0$ and consequently $\eta_c=0$, it is straight forward to see that $a \leq 0$, $b<0$ and $c<0$. Thus, $\partial{\Rnum}/\partial{\omega} \geq 0$. 
As an example, in the case of a very accurate testing regime,  i.e., $P_I=1$, $a \geq 0$ is achieved. If $a\geq 0$, the quadratic expression in \eqref{Rom}, has Real roots. Assuming that $\omega_1<0$ and $\omega_2>0$ be the roots of the quadratic expression in $\partial{R_0}/\partial{\omega}$. Thus, $\partial{R_0}/\partial{\omega}>0$ for $0<\omega<\omega_2$ and  $\partial{R_0}/\partial{\omega}<0$ for $\omega>\omega_2$.

>>>>

The block matrix $G_{12}$ does not influence $\Rnum$ (defined as the spectral radius of $G$). All that matters here are the eigenvalues of $G_{11}$, which are 0 and $\Rnum$ \eqref{R0}.

% %%%%%%%
\subsection{On Testing Rate and Numerical Singularity}

\bmb{this should go in the main methods section, I think}

The testing rate, $\sigma$, should be formulated such that people from the untested compartments will not be tested if they are not there. The numerical singularity issue with the chosen $\sigma$ \eqref{sigma} is that the population in $S$ compartments appeared to blow up when the DFE is achieved. This is once the only untested people are susceptibles, the FOI will become $\Lambda=0$, testing rate $F_s=\rho N_0/S_u$. Thus, eq(1) of the model will be $d S_u/dt = - \rho N_0 + \omega S_n$ which is no longer dependent on $S_u$ and a linear rate of leaving the $S_u$ compartment.

@@

In the case of ``perfect isolation'', i.e., when $\eta_w=0$ and consequently $\eta_c=0$, it is straightforward to see that $a \leq 0$, $b<0$ and $c<0$. Thus, $\partial{\Rnum}/\partial{\omega} \geq 0$. 
As an example, in the case of a very accurate testing regime,  i.e., $P_I=1$, $a \geq 0$ is achieved. If $a\geq 0$, the quadratic expression in \eqref{Rom}, has Real roots. Assuming that $\omega_1<0$ and $\omega_2>0$ be the roots of the quadratic expression in $\partial{R_0}/\partial{\omega}$. Thus, $\partial{R_0}/\partial{\omega}>0$ for $0<\omega<\omega_2$ and  $\partial{R_0}/\partial{\omega}<0$ for $\omega>\omega_2$.
